`r params$doc_title`

### 2022-12-16 scripts/MSc.Rmd
changed standard deviation from which coefficients are drawn in simstudy.R

@@

# 4. Exclude the IV if Pval > genome-wide significance threshold  (5 × 10−8)
pvals_df %>% 
  summarize(across(.cols = everything(), function(x) sum(x < 5*10^(-6)))) %>% 
  t() %>% 
  kable(caption = "Count of significant SNPs depending on sample size")

@@

         ),
         explained_variance_GSD = explained_variance_binary(PA = eaf.gsd, 
                                                            RR1 = exp(beta.gsd), 
                                                            RR2 = exp(beta.gsd)^2, 
                                                            K = 0.1  # assumed prevalence in population
                                                            )$Vg,
         explained_variance_GBC = explained_variance_binary(PA = eaf.gbc, 
                                                            RR1 = exp(beta.gbc), 
                                                            RR2 = exp(beta.gbc)^2, 
                                                            K =1.2/100000  # assumed prevalence in population
                                                            )$Vg,
         explained_variance_GBC2 = explained_variance_binary(PA = eaf.gbc, 
                                                            RR1 = exp(beta.gbc), 
                                                            RR2 = 1+(2*(exp(beta.gbc)-1)), 
                                                            K =1.2/100000  # assumed prevalence in population
                                                            )$Vg

         )
```

@@

```{r}
ggplot(data=my_data_harm, aes(x=explained_variance_BMI, y=explained_variance_BMI2)) +
  geom_point(alpha=0.6)+
  geom_abline()+
  theme_few()
```

@@

for (i in 1:length(colnames_pval) ) {
  threshold <- 5*10^(-6)
  select_col <- colnames_pval[i]
  # calculate cum explained variance and count of IVs
  summarydat <- my_data_harm %>% 
    filter(!!sym(select_col) < threshold) %>% 
    select(explained_variance_BMI, explained_variance_BMI2, explained_variance_GSD, explained_variance_GBC) %>% 
    summarise(expl_variances =across(.cols = everything(), function(x) sum(x)),
              count_IVs = n())
  # fill up df
  df_cum_expl_var[i, 2] <- summarydat$expl_variances[1]
  df_cum_expl_var[i, 3] <- summarydat$expl_variances[2]
  df_cum_expl_var[i, 4] <- summarydat$expl_variances[3]
  df_cum_expl_var[i, 5] <- summarydat$expl_variances[4]
  df_cum_expl_var[i, 6] <- summarydat$count_IVs
}
```

>>>>

-   2022-12-05
    1. How did the large CI for the simulated PVEs arise? The simulated beta coefficients were drawn from given betas **AND** sample-size adjusted standard errors `*get simulated se_{sample size}*`. Therefore, for small sample sizes we yielded large variance for the beta coefficients. I changed the simulation and only used the given standard errors for our simulation scenarios in "scripts/simstudy.R".

@@

# 4. Exclude the IV if Pval > genome-wide significance threshold  (5 × 10−8) --> updated to 5 × 10−6
pvals_df %>% 
  summarize(across(.cols = everything(), function(x) sum(x < 5*10^(-6)))) %>% 
  t() %>% 
  kable(caption = "Count of significant SNPs depending on sample size")

@@

         ),
         explained_variance_GSD = explained_variance_binary(PA = eaf.gsd, 
                                                            RR1 = exp(beta.gsd), 
                                                            RR2 = exp(beta.gsd)^2, 
                                                            K = 0.1  # assumed prevalence in population
                                                            )$Vg,
         explained_variance_GBC2 = explained_variance_binary(PA = eaf.gbc, 
                                                            RR1 = exp(beta.gbc), 
                                                            RR2 = exp(beta.gbc)^2, 
                                                            K =1.2/100000  # assumed prevalence in population
                                                            )$Vg,
         explained_variance_GBC = explained_variance_binary(PA = eaf.gbc, 
                                                            RR1 = exp(beta.gbc), 
                                                            RR2 = 1+(2*(exp(beta.gbc)-1)), 
                                                            K =1.2/100000  # assumed prevalence in population
                                                            )$Vg

         )

sum(my_data_harm$explained_variance_GBC)
sum(my_data_harm$explained_variance_GBC2)
```

@@

```{r compare-formulas-numeric-pve}
ggplot(data=my_data_harm, aes(x=explained_variance_BMI, y=explained_variance_BMI2)) +
  geom_point(alpha=0.6)+
  geom_abline()+
  theme_few()
```

@@

for (i in 1:length(colnames_pval) ) {
  threshold <- 5*10^(-6)
  select_col <- colnames_pval[i]
  # calculate cum explained variance and count of IVs
  summarydat <- my_data_harm %>% 
    filter(!!sym(select_col) < threshold) %>% 
    select(explained_variance_BMI, explained_variance_BMI2, explained_variance_GSD, explained_variance_GBC) %>% 
    summarise(expl_variances =across(.cols = everything(), function(x) sum(x, na.rm = TRUE)),
              count_IVs = n())
  # fill up df
  df_cum_expl_var[i, 2] <- summarydat$expl_variances[1]
  df_cum_expl_var[i, 3] <- summarydat$expl_variances[2]
  df_cum_expl_var[i, 4] <- summarydat$expl_variances[3]
  df_cum_expl_var[i, 5] <- summarydat$expl_variances[4]
  df_cum_expl_var[i, 6] <- summarydat$count_IVs
}
```
